---
title: "Kruskal-Wallis and Post-hoc"
date: "Last compiled on `r format(Sys.time(), '%d %b, %Y')`"
output:
  rmdformats::readthedown:
    self_contained: true
    thumbnails: false
    lightbox: false
    toc_depth: 5
    code_folding: hide
editor_options:
  chunk_output_type: inline
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE, warning = FALSE)
```

```{r include=FALSE}
# Install and load packages
packages <- c(
  "tidyverse",
  "httr",
  "table1",
  "patchwork",
  "skimr",
  "psych",
  "gt",
  "table1",
  "purrr",
  "dunn.test",
  "reshape2", #for melt 
  "rio", #package for importing any kinds of dataset
  "broom", "AICcmodavg", "ggpubr", "rstatix"
  )

# Change to install = TRUE to install the required packages
pacman::p_load(packages, character.only = TRUE, install = TRUE)

theme_set(theme_minimal())
```


```{r}
#cluster_dat <- rio::import(here::here("C:/Users/Wang Jiaxuan/OneDrive - Singapore University of Technology and Design/ORS/02 Community Survey/dataset/segmentation/2 factor/2 factor solution/kmeans_2_factors_FA_clusters4_lifestyle_15feb24.csv")) 
cluster_dat <- rio::import(here::here("C:/Users/Wang Jiaxuan/OneDrive - Singapore University of Technology and Design/ORS/02 Community Survey/dataset/segmentation/4 factor/4 factor solution/kmeans_4_factors_clusters4_lifestyle_14feb24.csv")) 
```

<!--## ANOVA-->

<!--```{r}
# Selecting numeric variables for the test
#numeric_vars <- cluster_dat %>% select(-(1:14), -(18:29), -"Income_Personal", -"Income_Household", -clusters) %>% colnames() # Removing the categorical variable

numeric_vars <- cluster_dat %>% select(-1,-(37:49), -(54:65),  -"Income_Personal", -"Income_Household", -clusters) %>%
  select("Health", "wellbeing", "nature_relatedness", everything())%>% colnames()
```-->

<!-- ```{r}
cluster_dat <- factor(cluster_dat$clusters)
aov_dat <- cluster_dat %>% select(-(1:14), -(18:29), -"Income_Personal", -"Income_Household")

aov_dat <- na.omit(aov_dat)

# boxplots and oneway-tests for the 4 variables at once
for (i in 1:36) { # variables to compare are variables 1 to 4
  boxplot(aov_dat[, i] ~ aov_dat$clusters, na.action = na.omit, # draw boxplots by group
    ylab = names(aov_dat[i]), # rename y-axis with variable's name
    xlab = "Clusters"
  )
  aov_res <- oneway.test(aov_dat[, i] ~ aov_dat$clusters, na.action = na.omit)
  cat("\nOne-way ANOVA for Cluster and ", names(aov_dat[, i]), ", the p-value is ", aov_res$p.value, "\n")
  #print(oneway.test(aov_dat[, i] ~ aov_dat$clusters, na.action = na.omit)) # print results of t-test
}
```-->

<!--```{r}
aov_dynamic <- function(df, group_col, var_cols) {
  results <- map(var_cols, ~{
    test_result <- oneway.test(reformulate(group_col, response = .x), data = df)
    tibble(variable = .x, p_value = round(test_result$p.value, 3), Test = "One-way ANOVA")
  }) %>%
    bind_rows()
  return(results)
}
```-->

<!--```{r}
aov_dynamic <- aov_dynamic(cluster_dat, "clusters", numeric_vars)
print(aov_dynamic) %>% gt()
#print(aov_dynamic) %>% gt() %>% gtsave("2 factor/ANOVA_2factors.docx")
print(aov_dynamic) %>% gt() %>% gtsave("4 factor/ANOVA_4factors.docx")
```-->

<!--### Post hoc test
Tukey Honest Significant Differences
<!--```{r}
TukeyHSD(aov(wellbeing ~ factor(clusters)
             , data = aov_dat), 
         conf.level=.95)

plot(TukeyHSD(aov(wellbeing ~ factor(clusters)
             , data = aov_dat), conf.level=.95), las = 2)
```-->





## Kruskal Wallis Test

```{r}
# Selecting numeric variables for the test
#numeric_vars <- cluster_dat %>% select(-(1:14), -(18:29), -"Income_Personal", -"Income_Household", -clusters) %>% colnames() # Removing the categorical variable

numeric_vars <- cluster_dat %>% select(-1,-(37:49), -(54:65),  -"Income_Personal", -"Income_Household", -clusters) %>%
  select("Health", "wellbeing", "nature_relatedness", everything())%>% colnames()
```

```{r}
kruskal_test_dynamic <- function(df, group_col, var_cols) {
  results <- map(var_cols, ~{
    test_result <- kruskal.test(reformulate(group_col, response = .x), data = df)
    tibble(variable = .x, p_value = round(test_result$p.value, 3), Test = "Kruskal-Wallis")
  }) %>%
    bind_rows()
  return(results)
}
```

```{r}
# Apply Kruskal-Wallis test
kruskal_results_dynamic <- kruskal_test_dynamic(cluster_dat, "clusters", numeric_vars)
print(kruskal_results_dynamic) %>% gt()
#print(kruskal_results_dynamic) %>% gt() %>% gtsave("2 factor/Kruskal_Wallis_2factors.docx")
#print(kruskal_results_dynamic) %>% gt() %>% gtsave("4 factor/Kruskal_Wallis_4factors.docx")
```

- Here, please highlight the variables with significant differences between the clusters



### Post hoc test


- For those scales returned significant result, conduct post hoc test (using Dunn's test) to determine which cluster is significantly different from which

```{r}
dunn.test::dunn.test(
  cluster_dat$Perceived_Interruption,
  cluster_dat$clusters,
  method = "holm"
)
```

```{r}
dunn_test(data = kw_dat, Health ~ clusters, p.adjust.method = "holm")-> dunn_res
kruskal_test(Health ~ clusters, data = kw_dat, na.action = na.omit) -> kru_res
dunn_res <- dunn_res %>% add_xy_position(x = "clusters") 
ggplot(kw_dat, mapping = aes(x = clusters, y = Health))+
  geom_boxplot(outlier.shape = NA, na.rm = TRUE) +
  stat_boxplot(mapping = aes(x = clusters, y = Health), geom='errorbar', 
               linetype=1, width=0.3)+  #whiskers
  stat_pvalue_manual(dunn_res, hide.ns = TRUE, 
                     bracket.nudge.y = 0.3, 
                     step.increase = 0.04,
                     coord.flip = TRUE)+
  labs(
    title = "Health",
    subtitle = get_test_label(kru_res, detailed = TRUE)
    #,caption = get_pwc_label(dunn_res)
  )  +
  coord_flip()+
  theme(plot.title = element_text(hjust = 0.5),
        plot.subtitle = element_text(size = 8),
        axis.title.x = element_blank())
#ggboxplot(kw_dat, x = "clusters", y = "Health", 
#          notch = FALSE, bxp.errorbar = TRUE,
#          outlier.shape = NA,
#          theme = ggplot2::theme_minimal()) + 
#  stat_pvalue_manual(dunn_res, hide.ns = TRUE, bracket.nudge.y = 0.3, 
#                     coord.flip = TRUE, tip.length = 0.03)+
#  labs(
#    sustitle = get_test_label(kru_res, detailed = TRUE),
#    caption = get_pwc_label(dunn_res)
#  ) +
#  coord_flip()
```

```{r}
kw_dat <- cluster_dat %>% select(-1,-(37:49), -(54:65),  -"Income_Personal", -"Income_Household") %>%
  select("Health", "wellbeing", "nature_relatedness", everything(), "clusters")
kw_dat$clusters <- as.factor(kw_dat$clusters)

### Need to place cluster variable as the last variable
mass_kwplot <- function(data, yvars){
  plot_list = list()
  
  for (i in yvars){
    kru_res <- kruskal_test(data[i] ~ data[ncol(data)], data = data, na.action = na.omit)
    dunn_res <- dunn_test(data = data, data[i] ~ data[ncol(data)], p.adjust.method = "holm")
    p <- ggplot(data, mapping = aes(x = data[ncol(data)], y = data[i])) + 
      geom_boxplot()+
      stat_pvalue_manual(dunn_res, hide.ns = TRUE, bracket.nudge.y = 0.3) +
      labs(
        title = print(names(data[i])),
        subtitle = get_test_label(kru_res, detailed = TRUE)
      ) + 
      coord_flip()
    
    plot_list[[i]] <- p
  }
  
  kwplot_facet <- ggarrange(plotlist=plot_list, ncol = 4)
  return(kwplot_facet)
}

```

```{r}
kw_yvars <- kw_dat %>% select(-37) %>% colnames()
mass_kwplot(kw_dat, "clusters", kw_yvars)
```

```{r}
mass_kwplot <- function(df, group_col, var_cols) {
  plot_list <- list()
  
  for (var_col in var_cols) {
    # Perform Kruskal-Wallis test
    kruskal_res <- kruskal_test(reformulate(group_col, response = var_col), data = df)
    # Perform dunn test
    dunn_res <- dunn_test(data = df, reformulate(group_col, response = var_col), p.adjust.method = "holm")
    dunn_res <- dunn_res %>% add_xy_position(x = group_col)
    
    # If significant, perform Dunn's test
    p<- ggplot(df, mapping = aes(x = group_col , y = var_col))+
      geom_boxplot(outlier.shape = NA, na.rm = TRUE) +
      stat_boxplot(mapping = aes(x = group_col, y = var_col), geom='errorbar', 
                   linetype=1, width=0.3)+  #whiskers
      stat_pvalue_manual(dunn_res, hide.ns = TRUE, 
                         bracket.nudge.y = 0.3, 
                         step.increase = 0.04,
                         coord.flip = TRUE)+
      labs(
           title = names(var_col)
           #, subtitle = get_test_label(kru_res, detailed = TRUE)
           #,caption = get_pwc_label(dunn_res)
      )  +
      coord_flip()+
      theme(plot.title = element_text(hjust = 0.5),
            plot.subtitle = element_text(size = 8),
            axis.title.x = element_blank())
    
    plot_list[[var_col]] <- p
  }
  
  kwplot_facet <- ggarrange(plotlist=plot_list, ncol = 6, nrow = 6, 
                            labels = NULL)
  return(kwplot_facet)
}

```


- Repeat the above test for all the variables with significance. The following functions can be used

```{r}
perform_posthoc_analysis <- function(df, group_col, var_cols) {
  results <- list()
  
  for (var_col in var_cols) {
    # Perform Kruskal-Wallis test
    kruskal_res <- kruskal.test(reformulate(group_col, response = var_col), data = df)
    cat("Kruskal-Wallis Test for", var_col, "\n")
    print(kruskal_res)
    
    # If significant, perform Dunn's test
    if (kruskal_res$p.value < 0.05) {
      cat("\nPerforming Dunn's post hoc test for", var_col, "due to significant Kruskal-Wallis test result.\n")
      dunn_res <- dunn.test(x = df[[var_col]], g = df[[group_col]], method = "bonferroni")
      results[[var_col]] <- dunn_res$res
      print(dunn_res)
    } else {
      cat("\nNo significant differences found for", var_col, ", so no post hoc test performed.\n")
    }
  }
  
  return(results)
}

# Identify numeric variables (excluding the group variable)
#numeric_vars <- cluster_dat %>% select(-(1:14), -(18:29), -"Income_Personal", -"Income_Household", -clusters)

# Run the analysis
posthoc_results <- perform_posthoc_analysis(cluster_dat, "clusters", numeric_vars)
```

