---
title: "Lifestyle segmentations"
author: "Jiaxuan"
date: "Last compiled on `r format(Sys.time(), '%d %b, %Y')`"
output:
  rmdformats::readthedown:
    self_contained: true
    thumbnails: false
    lightbox: false
    toc_depth: 5
    code_folding: hide
editor_options:
  chunk_output_type: inline
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, message=FALSE, warning=FALSE)
```

```{r}
# Install and load packages
packages <- c(
  "tidyverse",
  "httr",
  "table1",
  "patchwork",
  "skimr",
  "psych",
  "corrplot",
  "car",
  "factoextra",
  "gt",
  "table1",
  "lavaan",
  "mirt",
  "Rtsne",
  "cluster", #for PAM
  "reshape2", #for melt 
  "rio" #package for importing any kinds of dataset
  )

# Change to install = TRUE to install the required packages
pacman::p_load(packages, character.only = TRUE, install = TRUE)

library(factoextra)

theme_set(theme_minimal())
```

```{r}
#df <- read_csv("C:/Users/Wang Jiaxuan/OneDrive - Singapore University of Technology and Design/ORS/02 Community Survey/dataset/raw data/ORS_cleaned_V8_label.csv")
raw_dat <- read_csv("C:/Users/Wang Jiaxuan/OneDrive - Singapore University of Technology and Design/ORS/02 Community Survey/dataset/raw data/ORS_cleaned_V8.csv")

nr_df <- read_csv("C:/Users/Wang Jiaxuan/OneDrive - Singapore University of Technology and Design/ORS/02 Community Survey/dataset/segmentation/2 factor/2 factor solution/kmeans_2_factors_FA_clusters4_lifestyle_15feb24.csv") %>%
  select(id, nature_relatedness, wellbeing)
```


```{r}
lvl1 <- c('102'=-2, '101'=-1, '0'=0, '1'=1, '2' =2)
lifestyle_dat_0 <- raw_dat %>%
  select(1, starts_with("Lifestyle")) %>%
  mutate_all(as.factor)

recode <- function(x){
  y<- x+3
  return(y)
}

lifestyle_dat_3 <- lifestyle_dat_0 %>% 
  column_to_rownames(var ="id") %>% 
  likert2int(., levels = lvl1) %>%  
  mutate(Lifestyle_10=Lifestyle_10*-1) %>% #view() #reverse coding 10
  mutate_all(recode) #%>% #view() rownames_to_column(var="id") 

lifestyle_dat_2 <- lifestyle_dat_3 %>%
  rownames_to_column(var = "id") %>%
  mutate(id = as.double(id))


df0 <- raw_dat %>%
  select(-starts_with("Lifestyle"), -starts_with("Feeling_"))%>%
  left_join(nr_df, by = "id") %>%
  mutate(AgeGroup = as.factor(AgeGroup),
         Ethnicity = as.factor(Ethnicity_Cleaned),
         Gender = as.factor(Gender))

```


# KMO
```{r}
KMO(r=cor(lifestyle_dat_3))
```

## Bartlett’s test of sphericity
```{r}
cortest.bartlett(lifestyle_dat_3)
```

# 2 factors FA
```{r}
fafitfree <- lifestyle_dat_3 %>% scale() %>% fa(nfactors = 2, rotate = "oblimin", fm="ml")


n_factors <- length(fafitfree$e.values)

scree     <- data.frame(
  Factor_n =  as.factor(1:n_factors), 
  Eigenvalue = fafitfree$e.values)

ggplot(scree, aes(x = Factor_n, y = Eigenvalue, group = 1)) + 
  geom_point() + geom_line() +
  xlab("Number of factors") +
  ylab("Initial eigenvalue") +
  labs( title = "Scree Plot", 
        subtitle = "(Based on the unreduced correlation matrix)")
```

```{r}
fafitfree[["loadings"]]
#fafitfree["RMSEA"]
```


## Loading plot
```{r}
fafitfree[['scores']] %>%
  unclass() %>%
  as_tibble(rownames = "variables") %>%  # convert loadings to a tibble or easy plotting
  ggplot(aes(x = ML1, y = ML2)) + #Selecting factors for X and Y
  geom_text(aes(label = variables))
```

```{r}
lifestyle_fa <- lifestyle_dat_3 %>% scale() %>% 
  fa(nfactors = 2, rotate = "oblimin", fm="ml")

lifestyle_fa %>% 
  #principal(nfactors = 2, rotate = "oblimin") %>%
  pluck("scores")  %>%
  unclass()%>%
  as_tibble(rownames = "id") -> fa_df
fa_df %>%
  mutate(id = as.double(id))-> fa_df

fa_data <- fa_df %>%
  column_to_rownames(var = "id")
```


# fit 1 K-means
/ FA on lifestyle [k-means]

```{r}
factoextra ::fviz_nbclust(fa_data, kmeans, method = "silhouette")
```

<!--```{r}
hierarchical_clusters <- hclust(dist(cluster_data))
#fviz_dend(hierarchical_clusters, k = 4, cex = 0.4) # K= the number of clusters in the dendogram
```-->


## K=2
```{r}
set.seed(1234)
kmeans_clusters <- kmeans(fa_data, centers = 2, nstart = 50) # selecting 4 clusters
fviz_cluster(kmeans_clusters, data = fa_data, ggtheme = theme_minimal()) 
```

```{r}
cluster_data <- kmeans_clusters$cluster %>% #view()
  as_tibble(rownames = "id") %>%
  rename("clusters" = value) %>% 
  mutate(id=as.numeric(id)) %>% 
  data.frame()
```

## Description
```{r}
seg_dat <- cluster_data %>%
  left_join(lifestyle_dat_2, by = "id") %>%
  left_join(fa_df, by = "id") %>%
  left_join(df0, by = "id")
```

```{r}
seg_dat %>%
  group_by(clusters)%>% 
  summarise(count=n())
```

```{r}

df_long_1 <- seg_dat %>% 
  select(Favourite_StayDuration,Favourite_VisitFrequency,General_Accessibility,
         General_Affordability, General_TravelTime, General_VisitFrequency,
         Health, wellbeing, InformalORS_Importance, nature_relatedness, 
         NearbyORS_VisitFrequency, PostCovid_Visit, clusters) %>%
    pivot_longer(
    cols = -clusters, # Select all columns except for Group for pivoting
    names_to = "Scale", # Name of the new column for the scale names
    values_to = "Value" # Name of the new column for the values
  )

df_long_stsfc <- seg_dat %>% select(starts_with("Satisfaction_"), clusters) %>%
    pivot_longer(
    cols = -clusters, # Select all columns except for Group for pivoting
    names_to = "Scale", # Name of the new column for the scale names
    values_to = "Value" # Name of the new column for the values
  )

df_long_benefits <- seg_dat %>% select(starts_with("Benefits_"), clusters) %>%
    pivot_longer(
    cols = -clusters, # Select all columns except for Group for pivoting
    names_to = "Scale", # Name of the new column for the scale names
    values_to = "Value" # Name of the new column for the values
  )

df_long_lifestyle <- seg_dat %>% select(starts_with("Lifestyle_"), clusters) %>% #view()
    pivot_longer(
    cols = -clusters, # Select all columns except for Group for pivoting
    names_to = "Scale", # Name of the new column for the scale names
    values_to = "Value" # Name of the new column for the values
  )

df_long_fa <- seg_dat %>% select(starts_with("ML"), clusters) %>% #view()
    pivot_longer(
    cols = -clusters, # Select all columns except for Group for pivoting
    names_to = "Scale", # Name of the new column for the scale names
    values_to = "Value" # Name of the new column for the values
  )
  
```


```{r}
ggplot(df_long_lifestyle, aes(x = as.factor(clusters), y = Value, fill = as.factor(clusters))) + 
  geom_boxplot() + 
  facet_wrap(facets = ~ (factor(Scale, 
                                levels = c("Lifestyle_1", "Lifestyle_2", "Lifestyle_3", "Lifestyle_4", 
                                           "Lifestyle_5", "Lifestyle_6", "Lifestyle_7", "Lifestyle_8", 
                                           "Lifestyle_9", "Lifestyle_10", "Lifestyle_11", "Lifestyle_12"))),
             scales = "free_y") + # Allows different y scales for each scale 
  labs(title = "Boxplots by Clusters and Lifestyle", 
       x = "Clusters", 
       y = "", 
       fill = "Cluster") +
  scale_fill_manual(values = c("#EDDCA2", "#F69DA4", "#8AAEDB", "#AAD7A5"))
  #scale_fill_brewer(palette = "Set3")
```

#### Box Plots and Descriptive Tables

```{r}
table1(~ML1 + ML2 | clusters, data = seg_dat)
```


```{r}
table1(~ Lifestyle_1+ Lifestyle_2+Lifestyle_3+Lifestyle_4+Lifestyle_5+
         Lifestyle_6+Lifestyle_7+Lifestyle_8+Lifestyle_9+Lifestyle_10+
         Lifestyle_11+Lifestyle_12| clusters, #for grouping
data = seg_dat
)
```

```{r}
table1(~ Gender + Ethnicity + AgeGroup + Income_Personal + Income_Household | clusters, #for grouping
data = seg_dat
)
```

```{r}
ggplot(df_long_1, aes(x = as.factor(clusters), y = Value, fill = as.factor(clusters))) + 
  geom_boxplot() + 
  facet_wrap(~ Scale, scales = "free_y") + # Allows different y scales for each scale
  labs(title = "Boxplots by Clusters and Scale", 
       x = "Clusters", 
       y = "", 
       fill = "Cluster") +
  scale_fill_manual(values = c("#EDDCA2", "#F69DA4", "#8AAEDB", "#AAD7A5"))
```

```{r}
ggplot(df_long_stsfc, aes(x = as.factor(clusters), y = Value, fill = as.factor(clusters))) + 
  geom_boxplot() + 
  facet_wrap(~ Scale, scales = "free_y") + # Allows different y scales for each scale
  labs(title = "Boxplots by Clusters and Scale", 
       x = "Clusters", 
       y = "", 
       fill = "Cluster") +
  scale_fill_manual(values = c("#EDDCA2", "#F69DA4", "#8AAEDB", "#AAD7A5", "#999999"))
```

```{r}
ggplot(df_long_benefits, aes(x = as.factor(clusters), y = Value, fill = as.factor(clusters))) + 
  geom_boxplot() + 
  facet_wrap(~ Scale, scales = "free_y") + # Allows different y scales for each scale
  labs(title = "Boxplots by Clusters and Scale", 
       x = "Clusters", 
       y = "", 
       fill = "Cluster") +
  scale_fill_manual(values = c("#EDDCA2", "#F69DA4", "#8AAEDB", "#AAD7A5", "#999999"))
```

# fit 2 K-mediod
/ FA on lifestyle +sociodemo  [k-medoid]
```{r}
lifestyle_dat <- df0 %>%
  select(id, AgeGroup, Ethnicity, Gender) %>%
  left_join(fa_df) %>%
  column_to_rownames(var="id")
```

```{r}
gower_dist <- 
  lifestyle_dat %>% 
    daisy(metric = "gower")
```

k=4
```{r}
sil_width <- c(NA)
for (i in 2:8) {  #exploring the number of clusters from 2 to 8
  pam_fit      <- pam(gower_dist, diss = TRUE, k = i)  
  sil_width[i] <- pam_fit$silinfo$avg.width  
}
```

```{r}
#Plotting silhouette
sil_width %>% 
  as_tibble() %>% 
   rowid_to_column() %>% 
   filter(rowid %in% c(2:8)) %>% 
   ggplot(aes(rowid, value)) +
   geom_line(colour  = 'black', size = 0.7) +
   geom_point(colour = 'black', size = 1.3) +
   labs(title = 'Silhouette Widths of k-medoid Clusters',
        x     = "Number of clusters",
        y     = 'Silhouette Width') +
   theme(plot.title = element_text(hjust = 0.5))
```

## k = 4
### Visualizing Cluster

```{r}
set.seed(123)

pam.res <- 
  gower_dist  %>% 
    pam(k = 4, diss = TRUE)
```

```{r}
tsne_obj <- Rtsne(gower_dist , is_distance = TRUE)
tsne_obj$Y %>%
  data.frame() %>%
  setNames(c("X", "Y")) %>%
  mutate(cluster = factor(pam.res$clustering)) %>% 
  # plot
  ggplot(aes(x = X, y = Y, colour = cluster)) +
  geom_point()  +
  theme_light() +
  labs(title     = 't-SNE 2D Projections of k-medoid Clusters')  +
  theme(plot.title = element_text(hjust = 0.5))
```

```{r}
cluster_data <- cbind(lifestyle_dat, cluster = pam.res$cluster) %>% data.frame() %>% 
  rename(clusters = cluster) %>% 
    mutate(clusters = as.factor(clusters)) %>% 
  rownames_to_column(var="id") %>% 
  select(id, clusters)
  
#head(df)
```

## Description
```{r}
cluster_data <- cluster_data %>%
  mutate(id = as.double(id))

seg_dat <- cluster_data %>%
  left_join(lifestyle_dat_2, by = "id") %>%
  left_join(fa_df, by = "id") %>%
  left_join(df0, by = "id")
```

```{r}
seg_dat %>%
  group_by(clusters)%>% 
  summarise(count=n())
```

```{r}
df_long_1 <- seg_dat %>% 
  select(Favourite_StayDuration,Favourite_VisitFrequency,General_Accessibility,
         General_Affordability, General_TravelTime, General_VisitFrequency,
         Health, wellbeing, InformalORS_Importance, nature_relatedness, 
         NearbyORS_VisitFrequency, PostCovid_Visit, clusters) %>%
    pivot_longer(
    cols = -clusters, # Select all columns except for Group for pivoting
    names_to = "Scale", # Name of the new column for the scale names
    values_to = "Value" # Name of the new column for the values
  )

df_long_stsfc <- seg_dat %>% select(starts_with("Satisfaction_"), clusters) %>%
    pivot_longer(
    cols = -clusters, # Select all columns except for Group for pivoting
    names_to = "Scale", # Name of the new column for the scale names
    values_to = "Value" # Name of the new column for the values
  )

df_long_benefits <- seg_dat %>% select(starts_with("Benefits_"), clusters) %>%
    pivot_longer(
    cols = -clusters, # Select all columns except for Group for pivoting
    names_to = "Scale", # Name of the new column for the scale names
    values_to = "Value" # Name of the new column for the values
  )

df_long_lifestyle <- seg_dat %>% select(starts_with("Lifestyle_"), clusters) %>% #view()
    pivot_longer(
    cols = -clusters, # Select all columns except for Group for pivoting
    names_to = "Scale", # Name of the new column for the scale names
    values_to = "Value" # Name of the new column for the values
  )

df_long_fa <- seg_dat %>% select(starts_with("ML"), clusters) %>% #view()
    pivot_longer(
    cols = -clusters, # Select all columns except for Group for pivoting
    names_to = "Scale", # Name of the new column for the scale names
    values_to = "Value" # Name of the new column for the values
  )
  
```


```{r}
ggplot(df_long_lifestyle, aes(x = as.factor(clusters), y = Value, fill = as.factor(clusters))) + 
  geom_boxplot() + 
  facet_wrap(facets = ~ (factor(Scale, 
                                levels = c("Lifestyle_1", "Lifestyle_2", "Lifestyle_3", "Lifestyle_4", 
                                           "Lifestyle_5", "Lifestyle_6", "Lifestyle_7", "Lifestyle_8", 
                                           "Lifestyle_9", "Lifestyle_10", "Lifestyle_11", "Lifestyle_12"))),
             scales = "free_y") + # Allows different y scales for each scale 
  labs(title = "Boxplots by Clusters and Lifestyle", 
       x = "Clusters", 
       y = "", 
       fill = "Cluster") +
  scale_fill_manual(values = c("#EDDCA2", "#F69DA4", "#8AAEDB", "#AAD7A5"))
  #scale_fill_brewer(palette = "Set3")
```

#### Box Plots and Descriptive Tables

```{r}
table1(~ML1 + ML2 | clusters, data = seg_dat)
```


```{r}
table1(~ Lifestyle_1+ Lifestyle_2+Lifestyle_3+Lifestyle_4+Lifestyle_5+
         Lifestyle_6+Lifestyle_7+Lifestyle_8+Lifestyle_9+Lifestyle_10+
         Lifestyle_11+Lifestyle_12| clusters, #for grouping
data = seg_dat
)
```

```{r}
table1(~ Gender + Ethnicity + AgeGroup + Income_Personal + Income_Household | clusters, #for grouping
data = seg_dat
)
```

```{r}
ggplot(df_long_1, aes(x = as.factor(clusters), y = Value, fill = as.factor(clusters))) + 
  geom_boxplot() + 
  facet_wrap(~ Scale, scales = "free_y") + # Allows different y scales for each scale
  labs(title = "Boxplots by Clusters and Scale", 
       x = "Clusters", 
       y = "", 
       fill = "Cluster") +
  scale_fill_manual(values = c("#EDDCA2", "#F69DA4", "#8AAEDB", "#AAD7A5"))
```

```{r}
ggplot(df_long_stsfc, aes(x = as.factor(clusters), y = Value, fill = as.factor(clusters))) + 
  geom_boxplot() + 
  facet_wrap(~ Scale, scales = "free_y") + # Allows different y scales for each scale
  labs(title = "Boxplots by Clusters and Scale", 
       x = "Clusters", 
       y = "", 
       fill = "Cluster") +
  scale_fill_manual(values = c("#EDDCA2", "#F69DA4", "#8AAEDB", "#AAD7A5", "#999999"))
```

```{r}
ggplot(df_long_benefits, aes(x = as.factor(clusters), y = Value, fill = as.factor(clusters))) + 
  geom_boxplot() + 
  facet_wrap(~ Scale, scales = "free_y") + # Allows different y scales for each scale
  labs(title = "Boxplots by Clusters and Scale", 
       x = "Clusters", 
       y = "", 
       fill = "Cluster") +
  scale_fill_manual(values = c("#EDDCA2", "#F69DA4", "#8AAEDB", "#AAD7A5", "#999999"))
```

# fit 3 K-mediod
/ FA on lifestyle +sociodemo+health and wellbeing  [k-medoid]
```{r}
lifestyle_dat <- df0 %>%
  select(id, AgeGroup, Ethnicity, Gender, Health, wellbeing) %>%
  left_join(fa_df) %>%
  column_to_rownames(var="id")
```

```{r}
gower_dist <- 
  lifestyle_dat %>% 
    daisy(metric = "gower")
```

k=4
```{r}
sil_width <- c(NA)
for (i in 2:8) {  #exploring the number of clusters from 2 to 8
  pam_fit      <- pam(gower_dist, diss = TRUE, k = i)  
  sil_width[i] <- pam_fit$silinfo$avg.width  
}
```

```{r}
#Plotting silhouette
sil_width %>% 
  as_tibble() %>% 
   rowid_to_column() %>% 
   filter(rowid %in% c(2:8)) %>% 
   ggplot(aes(rowid, value)) +
   geom_line(colour  = 'black', size = 0.7) +
   geom_point(colour = 'black', size = 1.3) +
   labs(title = 'Silhouette Widths of k-medoid Clusters',
        x     = "Number of clusters",
        y     = 'Silhouette Width') +
   theme(plot.title = element_text(hjust = 0.5))
```

## k = 4
### Visualizing Cluster

```{r}
set.seed(123)

pam.res <- 
  gower_dist  %>% 
    pam(k = 4, diss = TRUE)
```

```{r}
tsne_obj <- Rtsne(gower_dist , is_distance = TRUE)
tsne_obj$Y %>%
  data.frame() %>%
  setNames(c("X", "Y")) %>%
  mutate(cluster = factor(pam.res$clustering)) %>% 
  # plot
  ggplot(aes(x = X, y = Y, colour = cluster)) +
  geom_point()  +
  theme_light() +
  labs(title     = 't-SNE 2D Projections of k-medoid Clusters')  +
  theme(plot.title = element_text(hjust = 0.5))
```

```{r}
cluster_data <- cbind(lifestyle_dat, cluster = pam.res$cluster) %>% data.frame() %>% 
  rename(clusters = cluster) %>% 
    mutate(clusters = as.factor(clusters)) %>% 
  rownames_to_column(var="id") %>% 
  select(id, clusters)
  
#head(df)
```

## Description
```{r}
cluster_data <- cluster_data %>%
  mutate(id = as.double(id))

seg_dat <- cluster_data %>%
  left_join(lifestyle_dat_2, by = "id") %>%
  left_join(fa_df, by = "id") %>%
  left_join(df0, by = "id")
```

```{r}
seg_dat %>%
  group_by(clusters)%>% 
  summarise(count=n())
```

```{r}
df_long_1 <- seg_dat %>% 
  select(Favourite_StayDuration,Favourite_VisitFrequency,General_Accessibility,
         General_Affordability, General_TravelTime, General_VisitFrequency,
         Health, wellbeing, InformalORS_Importance, nature_relatedness, 
         NearbyORS_VisitFrequency, PostCovid_Visit, clusters) %>%
    pivot_longer(
    cols = -clusters, # Select all columns except for Group for pivoting
    names_to = "Scale", # Name of the new column for the scale names
    values_to = "Value" # Name of the new column for the values
  )

df_long_stsfc <- seg_dat %>% select(starts_with("Satisfaction_"), clusters) %>%
    pivot_longer(
    cols = -clusters, # Select all columns except for Group for pivoting
    names_to = "Scale", # Name of the new column for the scale names
    values_to = "Value" # Name of the new column for the values
  )

df_long_benefits <- seg_dat %>% select(starts_with("Benefits_"), clusters) %>%
    pivot_longer(
    cols = -clusters, # Select all columns except for Group for pivoting
    names_to = "Scale", # Name of the new column for the scale names
    values_to = "Value" # Name of the new column for the values
  )

df_long_lifestyle <- seg_dat %>% select(starts_with("Lifestyle_"), clusters) %>% #view()
    pivot_longer(
    cols = -clusters, # Select all columns except for Group for pivoting
    names_to = "Scale", # Name of the new column for the scale names
    values_to = "Value" # Name of the new column for the values
  )

df_long_fa <- seg_dat %>% select(starts_with("ML"), clusters) %>% #view()
    pivot_longer(
    cols = -clusters, # Select all columns except for Group for pivoting
    names_to = "Scale", # Name of the new column for the scale names
    values_to = "Value" # Name of the new column for the values
  )
  
```


```{r}
ggplot(df_long_lifestyle, aes(x = as.factor(clusters), y = Value, fill = as.factor(clusters))) + 
  geom_boxplot() + 
  facet_wrap(facets = ~ (factor(Scale, 
                                levels = c("Lifestyle_1", "Lifestyle_2", "Lifestyle_3", "Lifestyle_4", 
                                           "Lifestyle_5", "Lifestyle_6", "Lifestyle_7", "Lifestyle_8", 
                                           "Lifestyle_9", "Lifestyle_10", "Lifestyle_11", "Lifestyle_12"))),
             scales = "free_y") + # Allows different y scales for each scale 
  labs(title = "Boxplots by Clusters and Lifestyle", 
       x = "Clusters", 
       y = "", 
       fill = "Cluster") +
  scale_fill_manual(values = c("#EDDCA2", "#F69DA4", "#8AAEDB", "#AAD7A5"))
  #scale_fill_brewer(palette = "Set3")
```

#### Box Plots and Descriptive Tables

```{r}
table1(~ML1 + ML2 | clusters, data = seg_dat)
```


```{r}
table1(~ Lifestyle_1+ Lifestyle_2+Lifestyle_3+Lifestyle_4+Lifestyle_5+
         Lifestyle_6+Lifestyle_7+Lifestyle_8+Lifestyle_9+Lifestyle_10+
         Lifestyle_11+Lifestyle_12| clusters, #for grouping
data = seg_dat
)
```

```{r}
table1(~ Gender + Ethnicity + AgeGroup + Income_Personal + Income_Household | clusters, #for grouping
data = seg_dat
)
```

```{r}
ggplot(df_long_1, aes(x = as.factor(clusters), y = Value, fill = as.factor(clusters))) + 
  geom_boxplot() + 
  facet_wrap(~ Scale, scales = "free_y") + # Allows different y scales for each scale
  labs(title = "Boxplots by Clusters and Scale", 
       x = "Clusters", 
       y = "", 
       fill = "Cluster") +
  scale_fill_manual(values = c("#EDDCA2", "#F69DA4", "#8AAEDB", "#AAD7A5"))
```

```{r}
ggplot(df_long_stsfc, aes(x = as.factor(clusters), y = Value, fill = as.factor(clusters))) + 
  geom_boxplot() + 
  facet_wrap(~ Scale, scales = "free_y") + # Allows different y scales for each scale
  labs(title = "Boxplots by Clusters and Scale", 
       x = "Clusters", 
       y = "", 
       fill = "Cluster") +
  scale_fill_manual(values = c("#EDDCA2", "#F69DA4", "#8AAEDB", "#AAD7A5", "#999999"))
```

```{r}
ggplot(df_long_benefits, aes(x = as.factor(clusters), y = Value, fill = as.factor(clusters))) + 
  geom_boxplot() + 
  facet_wrap(~ Scale, scales = "free_y") + # Allows different y scales for each scale
  labs(title = "Boxplots by Clusters and Scale", 
       x = "Clusters", 
       y = "", 
       fill = "Cluster") +
  scale_fill_manual(values = c("#EDDCA2", "#F69DA4", "#8AAEDB", "#AAD7A5", "#999999"))
```









